Andres Karjus

### 2019-03-02 index.Rmd
poster description

- "Modelling lexical interactions in diachronic corpora": a poster to be presented at the [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html), here is an online [version with interactive plots](https://andreskarjus.github.io/isle_poster).

>>>>

- "Modelling lexical interactions in diachronic corpora": a poster to be presented at the [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html), here is an [online version with interactive plots](https://andreskarjus.github.io/isle_poster) and an extended appendix.
